Tables in the project

### 2018-11-15 paper/Tables/2by2Table1.Rmd
table for AJCN, 3.5+3.6 added

# Multilevel 2by2 table 1
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "P value [note]")

@@

# Day level only models
```{r echo=FALSE, message=FALSE, warning=FALSE}
# library(kableExtra)
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/ndns_level1only.csv", header = T)
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
dt[1,8] <- "--"
dt[2,8] <- "< 0.0001"
dt[3,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "latex", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)", 
      booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
# row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = c("Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC;" ,
                       "Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with", 
                       "q-1 classes models."))
```

# LCGA models table 1
```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/LCGA3Cresults.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")

@@

# Model fit criteria
```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Mixed_7slots.csv", header = T)
dt <- dt[,-7]
names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
dt[is.na(dt)] <- ""
# library(formattable)

@@

# Day level solution 1
```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/timeslots_cw3cb3_univariate.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Time slots of the day", "Responses of carbohydrate intake", "Frequency", "Precentages (%)", 
               "Class 1 (30.8%)", "Class 2 (39.8%)", "Class 3 (29.5%)")

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Daylevel.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "High carbohydrate day", "Low carbohydrate day", "Regular meals day", "P value[note]")

@@

```{r tab1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3results.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class = 2 (n = 1772)", "Individual class = 3 (n = 2653)", "P value [note]")

@@

```{r tab-nutri-indi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Carbslotcompo.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Low carbohydrate eaters (n = 1730)", "Moderate carbohydrate eaters (n = 1772)", "High carbohydrate eaters (n = 2653)", "P value[note]")

@@

```{r tab2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/Timeslots_CW3CB3table2_bmiDM.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class (n = 1772)", "Individual class 3 (n = 2653)", "P value[note]")

@@

```{r tab1hypetension, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensiontab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Non-hypertensive", "Hypertensive", "P value[note]", 
               "Non-hypertensive", "Hypertensive", "P value")

@@

```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")

@@

```{r tab1DM, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/DMtab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Non-diabetes", "Diabetes", "P value[note]", 
               "Non-diabetes", "Diabetes", "P value")

@@

```{r survgression, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/SurveyReg.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Models", "Low", "Moderate", "P value[note]", "High", "P value", "Models", "Low", "Moderate", "P value", "High", "P value")
dt[2, 1] <- c("Model 1[note]")
dt[2, 7] <- c("Model 1[note]")
dt[8, 1] <- c("Model 1[note]")
dt[8, 7] <- c("Live with partner[note]")
dt[14, 1] <- c("Model 1[note]")
dt[14, 7] <- c("Live with partner[note]")
dt[20, 1] <- c("Model 1[note]")
dt[20, 7] <- c("Model 1[note]")
kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>%
  group_rows("Hypertension", 1, 3) %>%
  group_rows("Hypertension in non-diabetics", 4, 6) %>% 
  group_rows("BMI", 7, 9) %>%
  group_rows("BMI in non-diabetics", 10, 12) %>%
    group_rows("WC", 13, 15) %>%
  group_rows("WC in non-diabetics", 16, 18) %>%
  group_rows("DM", 19, 21) %>%
   add_header_above(c(" ", "Men (n = 2537)" = 5, "Women (n = 3618)" = 6)) %>% 
  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.",
                       "DM was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.")) %>% 
  add_footnote(c("P values were obtained from wald tests from either linear regression models or logistic regression models.",
                "Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);", 
                "Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);", 
                "Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;", 
                "Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;", 
                "Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;", 
                "Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;", 
                "Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption, TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);", 
                "Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG."), 
               notation = "symbol")
```

@@

```{r tab2HYT, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensionReg.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
dt[2, 1] <- c("Model 1[note]")
# dt[3, 1] <- c("Model 2[note]")
dt[8, 1] <- c("Model 1[note]")
# dt[9, 1] <- c("Model 2[note]")

@@

```{r tab2BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab2.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")

@@

```{r tab2WC,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/WCtab2.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")

>>>>

# Multilevel 2by2 table 1
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
# dt <- read.csv("../../Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")
dt <- read.csv("../../Tablecsv/CW2CB2results.csv", header = T, row.names = NULL, colClasses = "character")

names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "P value [note]")

@@

# Day level only models
```{r echo=FALSE, message=FALSE, warning=FALSE}
# library(kableExtra)
dt <- read.csv("../../Tablecsv/ndns_level1only.csv", header = T)
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
dt[1,8] <- "--"
dt[2,8] <- "< 0.0001"
dt[3,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "latex", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)", 
      booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
# row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = c("Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC;" ,
                       "Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with", 
                       "q-1 classes models."))
```

# LCGA models table 1
```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("../../Tablecsv/LCGA3Cresults.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Latent class = 1", "Latent class = 2", "Latent class = 3", "P value [note]")

@@

# Model fit criteria
```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("../../Tablecsv/Mixed_7slots.csv", header = T)
dt <- dt[,-7]
names(dt) <- c("Model", "1 class", "2 classes",  "3 classes", "4 classes", "5 classes")
dt[is.na(dt)] <- ""
# library(formattable)

@@

# Day level solution 1
```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("../../Tablecsv/timeslots_cw3cb3_univariate.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Time slots of the day", "Responses of carbohydrate intake", "Frequency", "Precentages (%)", 
               "Class 1 (30.8%)", "Class 2 (39.8%)", "Class 3 (29.5%)")

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
dt <- read.csv("../../Tablecsv/Daylevel.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "High carbohydrate day", "Low carbohydrate day", "Regular meals day", "P value[note]")

@@

```{r tab1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/Timeslots_CW3CB3results.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class = 2 (n = 1772)", "Individual class = 3 (n = 2653)", "P value [note]")

@@

```{r tab-nutri-indi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/Carbslotcompo.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Low carbohydrate eaters (n = 1730)", "Moderate carbohydrate eaters (n = 1772)", "High carbohydrate eaters (n = 2653)", "P value[note]")

@@

```{r tab2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/Timeslots_CW3CB3table2_bmiDM.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Variables", "Individual class 1 (n = 1730)", "Individual class (n = 1772)", "Individual class 3 (n = 2653)", "P value[note]")

@@

```{r tab1hypetension, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/hypertensiontab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Non-hypertensive", "Hypertensive", "P value[note]", 
               "Non-hypertensive", "Hypertensive", "P value")

@@

```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")

@@

```{r tab1DM, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/DMtab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Non-diabetes", "Diabetes", "P value[note]", 
               "Non-diabetes", "Diabetes", "P value")

@@

```{r survgression, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/SurveyReg.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Models", "Low", "Moderate", "P value[note]", "High", "P value", "Models", "Low", "Moderate", "P value", "High", "P value")
dt[2, 1] <- c("Model 1[note]")
dt[2, 7] <- c("Model 1[note]")
dt[8, 1] <- c("Model 1[note]")
dt[8, 7] <- c("Live with partner[note]")
dt[14, 1] <- c("Model 1[note]")
dt[14, 7] <- c("Live with partner[note]")
dt[20, 1] <- c("Model 1[note]")
dt[20, 7] <- c("Model 1[note]")
kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>%
  group_rows("Hypertension", 1, 3) %>%
  group_rows("Hypertension in non-diabetics", 4, 6) %>% 
  group_rows("BMI", 7, 9) %>%
  group_rows("BMI in non-diabetics", 10, 12) %>%
    group_rows("WC", 13, 15) %>%
  group_rows("WC in non-diabetics", 16, 18) %>%
  group_rows("DM", 19, 21) %>%
   add_header_above(c(" ", "Men (n = 2537)" = 5, "Women (n = 3618)" = 6)) %>% 
  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.",
                       "DM was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.")) %>% 
  add_footnote(c("P values were obtained from wald tests from either linear regression models or logistic regression models.",
                "Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);", 
                "Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);", 
                "Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;", 
                "Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;", 
                "Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;", 
                "Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;", 
                "Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption, TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);", 
                "Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG."), 
               notation = "symbol")
```

@@

```{r tab2HYT, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/hypertensionReg.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
dt[2, 1] <- c("Model 1[note]")
# dt[3, 1] <- c("Model 2[note]")
dt[8, 1] <- c("Model 1[note]")
# dt[9, 1] <- c("Model 2[note]")

@@

```{r tab2BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/BMItab2.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")

@@

```{r tab2WC,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("../../Tablecsv/WCtab2.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
